---
title: "datacleaner_intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{datacleaner_intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(datacleaner)
```
#Introduction

The datacleaner package provides simple tools for cleaning and checking data frames in R.
It helps you quickly remove missing values, duplicates, empty columns, and generate a data quality report.

This vignette shows how to use all functions in the package
##1. Data Quality Report

The data_quality() function gives an overview of your dataset, including missing values and duplicate rows.
```{r}
data_quality(mtcars)
```
##2. Remove Duplicate Rows

The remove_duplicates() function removes duplicate rows from a dataset.

```{r}
remove_duplicates(mtcars)
```
##3. Remove Rows with Missing Values

The remove_na() function removes rows that contain NA values.
```{r}
remove_na(mtcars)
```
##4. Remove Empty Columns

The remove_empty() function removes columns that contain only missing values.
```{r}
remove_empty(mtcars)
```

